---
title: "Interlocutors preserve complexity in language" 
bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

author-information: > 
 \author{Madeline Meyers \and Daniel Yurovsky \\
         \texttt{\{mcmeyers, yurovsky\}@uchicago.edu} \\
        Department of Psychology \\ University of Chicago}

abstract: >
    Why do languages change? One possibility is they evolve in response to two competing pressures: (1) to be easily learned, and (2) to be effective for communication. In a number of domains (e.g. kinship categories, color terms), variation in the world's natural languages appears to be accounted for by different but near-optimal tradeoffs between these two pressures [@regier2015]. Models of these evolutionary processes have modeled transmission chains in which errors of learning by one agent become the language input for the subsequent generation. However, a critical feature of human language is that children do not learn in isolation. Rather, they learn in communicative interactions with caregivers who can draw inferences from their errorful productions to their intended interests. In a set of iterated learning experiments, we show that this supportive context can have a powerful stabilizing role in the development of artificial languages, allowing them to achieve higher levels of asymptotic complexity than they would by vertical transmission alone. 
    
keywords: >
    communication; language acquisition; language evolution; iterated learning
    
output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(tidyverse)
library(tidyboot)
library(directlabels)
library(lme4)
library(lmerTest)
library(devtools)
library(reshape2)
library(emdist)
library(feather)
library(here)
library(english)
library(broom)
library(broom.mixed)
library(papaja)
library(ggthemes)
library(gridExtra)

theme_set(theme_classic(base_size = 10))
colors <- ptol_pal()(4)
```

# Introduction

How do you ask a group of people where they are going in Spanish? In Spain, the answer depends on the group: you might ask “Donde van ustedes?” of a group of work colleagues, but to address your friends, you use the informal “Donde váis vosotros?” instead. In Mexican Spanish, this distinction has disappeared, and the “ustedes” form is used exclusively. Why did Spanish change in this way, simplifying and shedding the formal second person plural? One working theory is that languages evolve to adapt to two dynamic competing pressures: (1) ease of learning and transmission, and (2) effective communication [@lupyan-2010]. 

When children are learning language, they often make simplification errors [@bowerman-1982]. If a child is asking for her bottle, she may be unable to produce the canonical English label "bottle," and say "baba" instead. Because her caregivers can combine her errorful utterance with their beliefs about what she wants, they can nonetheless correctly interpret this as a request for the bottle. 

**STILL THINKING THROUGHT THIS, I DON'T THINK THIS IS QUITE RIGHT**


This simplification works well, until the child starts to learn her animal words, and calls a sheep "baba". Here, she is conforming to the language-learnability bias: if she calls both a bottle and a sheep "baba", she has one less word to remember. Does this child go through life believing that "baba" is the label for these disparate objects? It's possible. Perhaps, if she never has a need to discriminate between sheep and bottles, she might even pass this label on to her children. In this way, errors in language can be passed on to the next generation through transmission from one speaker to the next. This process reflects the needs of the language speakers: if a distinction between objects is not needed for effective communication, there is no need to retain complexity. 

Children are often the actors who drive language evolution [@senghas-2003], yet they differ from adults in their cognitive capabilities, namely, memory systems [@kempe-2015], interests and early vocabularies, and conversation partners. Even though children are skilled language learners, their developing cognitive systems prevent aspects of language that are difficult to learn and remember from being passed on -- pushing languages towards simplicity [@hudsonkam-2005; @senghas-2003]. But languages that become too simple can lose the ability to be effective for communication [@kirby-2014]. Indeed, we could not have "baba" become the label for every object. What enables languages to retain their communicative utility in the face of these learnability pressures? 
  
Most Americans grow up in a world where it is useful to discriminate sheep and bottles -- and they must learn the different labels for these objects. It is often caregivers, through their explicit interventions as well as their implicit modeling of correct language, who may be reintroducing descriptiveness into a language where it would otherwise be lost. Children’s language learning is greatly influenced by those around them -- especially the adults they talk to most. These caregivers control much of their child’s linguistic input, and are responsible for seeing that their children develop effective and useful systems of communication. Even the youngest children are not passive learners of language — they are active participants, engaging in conversations with their parents. These adults are experts both in the language and in the children themselves, as they understand the child’s intuitions, personality, and context. Caregivers play an important interpretive role in these interactions through their ability to understand the intended target of children’s errorful productions [@chouinard-2003]. Adults can explicitly correct their children's language errors in various ways (e.g., by interruptions or repeating the correct word/grammatical form) [@penner-1987]. Yet, children primarily learn language through listening to others talk, rather than explicit instruction [@romberg-2010]. Thus, parent's modeling of accurate language constructions can have a powerful effect on reducing children's language errors: over time, children fix their own mistakes because they have learned the correct constructions from their caregivers [@hudsonkam-2005]. By way of this feedback, both implicit and explicit, children's simplification errors are corrected, and children are able to acquire adult-like speech. Eventually, when a child grows to be an adult, they will not transmit the errors they had as a child, but the correct forms of speech they learned from their caregivers -- as long as learning the correct forms is useful and necessary. Thus, over the course of a lifetime, the child language learner grows to become a parent language teacher, correcting their own children's errors. These error reconstructions may be a mechanism by which more structure is retained in language over many lifetimes than children could sustain alone.  

## Using iterated learning to study language change

To model the impact of these competing pressures on language evolution in the laboratory, we use the iterated learning paradigm developed by @kirby-2014. In this paradigm, one participant is trained on a randomly-generated language--e.g, a set of words created by arbitrarily pairing syllables together. That participant is later asked to recall the language, but inevitably makes some errors. This participants' errorful output then becomes the input for the next participant, producing a transmission chain. This iterated learning process models the transmission of language across generations, with each participant unintentionally changing the language through their memory biases. 

This paradigm has been used productively across a number of studies of this kind of cross-generational transmission in both adults [e.g., @smith-2010; @verhoef-2014; @kirby-2014; @kirby-2007; @christiansen-2003], and children [@kempe-2015; @raviv-2018]. A few more recent studies have also compared languages evolved over multiple generations (vertical transmission) to languages evolved by iterated use in the same conversational partners [horizontal transmission, @kirby-2015]. However, participants in horizontal transmission had similar levels of knowledge and similar cognitive constraints. Children learning language in asymmetric knowledge situations, where their parent both knows more language and has an adult cognitive system (Figure \ref{fig:baseline_schem}). We predict that this asymmetry may have a unique role in the evolution of language, allowing languages to resist some of the simplifying pressure of ease of transmissibilty through adults' ability to keep structure in place temporarily while children develop. 

We adapted @kempe-2015's non-linguistic iterated learning paradigm to model the effect of introducing a secondary, error-correcting participant on the evolution of language. We hypothesize that these error-correctors (analogous to caregivers and teachers) are pivotal not only to an individual's successful language acquisition, but also to the evolution of the language as a whole. This is because those who correct mistakes and provide feedback are able to protect against the strong transmissibility (simplicity) bias in early language learners by re-introducing and preserving complexity in language. 

All experiments were pre-registered on Open Science Framework, and all data and code can be accessed at the following link: https://osf.io/guzyf/?view_only=43ee3fe87cf24c968c4377675c3bc580. 

```{r baseline_schem, fig.env = "figure", fig.align='center', set.cap.width=T, fig.height = 2.5, fig.width = 2, num.cols.cap=1, fig.cap = "In Experiments 1 and 2 follow the conventional iterated learning paradigm, where a novel language is transmitted vertically through successive learning and recall. In Experiment 3, an element of horizontal transmission is added to the paradigm: novel language learners' reproductions are subject to feedback from a secondary participant, and this production is passed to the subsequent learner.", fig.show='hold', cache = T}
img1 <-  rasterGrob(as.raster(readPNG("figs/baseline_schem2.png")), interpolate = FALSE)
img2 <-  rasterGrob(as.raster(readPNG("figs/dyad_schem3.png")), interpolate = FALSE)
grid.arrange(img1, img2, ncol = 2)
```

# Experiment 1: Replicating @kempe-2015

We began by replication Kempe, Gauvrit, and Forsyth's [-@kempe-2015] experiment using a nonlinguistic stimulus to study the evolution of structure. We had two motivations for using this paradigm. First, the structures in this paradigm lend themselves to algorithmic quantification of complexity. Second, @kempe-2015 used this paradigm successfully with children, and our goal was to test our hypothesis not just in adult-adult chains, but also in child-adult chains (ongoing). 

## Method

```{r read_data}
all_data <- read_feather(here("analysis/feathers/all_data_new.feather"))
model_data <- read_feather(here("analysis/feathers/model_data_new.feather"))
all_spread_data <- 
  read_feather(here("analysis/feathers/all_spread_data_new.feather"))  
all_bind_data <- read_feather(here("analysis/feathers/all_bind_data_new.feather")) 
```

### Participants 

```{r e1_data}
e1_data <- all_data %>% filter(type == "baseline") %>%
  distinct(unique_id, seed, generation) %>%
  filter(generation > 0)

e1_generations <- max(e1_data$generation)
e1_seeds <- max(e1_data$seed)
```

Participants in Experiment 1 were `r nrow(e1_data)` adults recruited on Amazon Mechanical Turk. These participants were dived into `r e1_seeds %>% words` diffusion chains, each of which had `r e1_generations %>% words` generations. Each participant gave informed consent. The task was approximately eight minutes long, and subjects were compensated $0.50 for their participation.

### Design and Procedure
```{r}
n_thrown <- read_csv(here("/data/adult_baseline_wthrown.csv")) %>%
 filter(seed != 3, seed != 1)
```

Participants in Experiment 1 were asked to re-create patterns on a grid. Subjects were informed that they would see a target grid appear on their computer screen for ten seconds, followed by a picture (a visual mask) displayed for three seconds. After the visual mask, participants viewed a blank 8x8 grid where they were given one minute to re-create the target grid. Participants could click on any cell in the grid to change its color, and could also remove any color placed. A counter on the screen showed how many cells had been colored, and it varied dynamically with the participant's clicks. After placing 10 colors, participants could click a button to advance to the next trial (See Figure \ref{fig:e2_withplots} for example grids). A timer was also displayed on the screen, and participants were given an audio cue when they had fifteen seconds left. 

Prior to completing one training and three practice trials, each participant completed 6 Experiment trials.  Participants in the first generation of each chain received the same initial grids for Experiment trials. These initial 8x8 grids were generated by randomly selecting 10 of the 64 possible cells to be filled. Participants in subsequent generations received as their targets the outputs produced by the previous participant in their chain. All participants received the same training and practice trials. In the preliminary training trial, subjects viewed two 8x8 grids side-by-side and were instructed to make the blank grid on the right match the target grid on the left. Participants were unable to progress to the practice and Experimental trials without reaching perfect accuracy on this first trial.

Participants' performance on the practice trials were used as an attention check to determine whether their data would be passed to the next participant. If the participant scored less than 75% accuracy on the last two practice trials, or if they failed to select 10 cells before time ran out, their outputs were not transmitted to the next generation. In Experiment 1, `r nrow(n_thrown %>% filter(is.na(thrown)==F)) %>% words` participants failed to meet these criteria and were excluded from analysis. 

## Analysis 

Our primary measures of interest were reproduction accuracy and pattern complexity. Reproduction accuracy serves as a proxy for transmissibility -- higher reproduction accuracies indicate that the "language" is easier to learn. Reproduction accuracy was computed as the proportion of targets out of 10 which were placed in the same location on the target and input grids.  

Complexity served as a proxy for descriptiveness. We followed @kempe-2015 in using several measures of complexity: algorithmic complexity, chunking, and edge length. Algorithmic complexity is calculated using the Block Decomposition Method, a measure of Kolmogorov-Chaitin Complexity applied to 2-dimensional patterns [@zenil-2014]. This measure computes the length of the shortest Turing machine program required to produce the observed pattern. The shorter the program, the simpler the pattern. Chunking is the number of groups of colored blocks which share an edge. The more groups of blocks, the easier the pattern is to transmit, and the lower its complexity is. Edge length is the total perimeter of the colored blocks. If all blocks were in one chunk, the edge length would be low, and the complexity of the pattern would be lower compared to if none of the chosen targets shared an edge. Implementation of these metrics was adapted from code provided by @gauvrit-2017. 

## Results and Discussion

```{r baseline_models}
e1_acc <- model_data %>%
  filter(type == "baseline", condition == "adult", trialCount > 3) %>%
  lmer(accuracy ~ generation + trialCount + (1|sub_id) + (1|trialDisplay), data = .)

e1_bdm <-all_bind_data %>%
   filter(type == "baseline", condition == "adult", trialCount > 3) %>%
  lmer(bdm_mean ~ generation + trialCount + (1|sub_id) +  (1|trialDisplay), data = .)

e1_chunk <-all_bind_data %>%
   filter(type == "baseline", condition == "adult", trialCount > 3) %>%
  lmer(chunking_mean ~ generation + trialCount + (1|sub_id) +  (1|trialDisplay), data = .)

e1_edge <-all_bind_data %>%
   filter(type == "baseline", condition == "adult", trialCount > 3) %>%
  lmer(edge_mean ~ generation + trialCount + (1|sub_id) +  (1|trialDisplay), data = .)
```

```{r baseline_parameters}
e1_acc_effects <- e1_acc %>%
  tidy() %>%
  filter(term == "generation") %>%
  select(term, estimate, statistic, p.value)

e1_bdm_effects <- e1_bdm %>%
  tidy() %>%
  filter(term == "generation") %>%
  select(term, estimate, statistic, p.value)

e1_chunk_effects <- e1_chunk %>%
  tidy() %>%
  filter(term == "generation") %>%
  select(term, estimate, statistic, p.value)

e1_edge_effects <- e1_edge %>%
  tidy() %>%
  filter(term == "generation") %>%
  select(term, estimate, statistic, p.value)
```

If iterated learning captures the hypothesized pressures of expressiveness and transmissibility, we predict that reproduction accuracy should increase, and complexity should decrease over generations. We tested these predictions with mixed-effects logistic regressions, predicting accuracy and all three measures of complexity separately from fixed effects of generation and trial number, and random intercepts for participant and initial grid (e.g. \texttt{accuracy $\sim$ generation + trial +  (1|subject) + (1|initialGrid)}. 

Reproduction accuracy increased significantly over generations ($\beta =$ `r e1_acc_effects %>% pull(estimate) %>% round(3)`, $t =$ `r e1_acc_effects %>% pull(statistic) %>% round(3)`, $p =$ `r e1_acc_effects %>% pull(p.value) %>% printp`). Figure \ref{fig:e1_acc_plot} shows the results for accuracy. Complexity on all three measure decreased significantly over generations, as shown by Figure \ref{fig:e1_bdm_plot} ($\beta_{BDM} =$ `r e1_bdm_effects %>% pull(estimate) %>% round(3)`, $t =$ `r e1_bdm_effects %>% pull(statistic) %>% round(3)`, $p =$ `r e1_bdm_effects %>% pull(p.value) %>% printp`; $\beta_{chunking} =$ `r e1_chunk_effects %>% pull(estimate) %>% round(3)`, $t =$ `r e1_chunk_effects %>% pull(statistic) %>% round(3)`, $p =$ `r e1_chunk_effects %>% pull(p.value) %>% printp`; $\beta_{edge} =$ `r e1_edge_effects %>% pull(estimate) %>% round(3)`, $t =$ `r e1_edge_effects %>% pull(statistic) %>% round(3)`, $p =$ `r e1_edge_effects %>% pull(p.value) %>% printp`). Trial Number, or how far along the subject was in the task, was not a significant predictor in any model. 

In line with @kempe-2015, we found that accuracy increased cross generations and complexity decreased on all three measures. However, this changed appeared to be non-linear, with later generations perhaps evolving less rapidly than later generations (Figure \ref{fig:e1_acc_plot}). We thus replicated this experiment again, but increased the number of generations from six to twelve to have the power to estimate the shape of the evolutionary functions.

```{r e1_acc_plot, fig.env = "figure", fig.align='center', set.cap.width=T, fig.height = 2, fig.width = 3.4, num.cols.cap=1, fig.cap = "Experiments 1 show increases in accuracy (measured by proportion of 10 targets placed correctly) across transmission generations.", cache = T}
e1_chains_acc <- model_data %>%
  filter(type =="baseline", trialCount > 3) %>%
  group_by(generation, seed) %>%
  summarise(empirical_stat = mean(accuracy))

e1_mean_acc <- e1_chains_acc %>%
  tidyboot_mean(empirical_stat)
  
ggplot(e1_mean_acc, aes(x = generation, y = empirical_stat)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), 
                  color = colors[1], size = 0.3) + 
  geom_smooth(se = F, color = colors[1], method = "lm") +
  ylab("Reproduction accuracy") +
  scale_x_continuous(limits = c(1,6), breaks=seq(1,6), name = "Generation")
```


```{r e1_bdm_plot, fig.env = "figure", fig.align='center', set.cap.width=T, fig.height = 2, fig.width = 3.4, num.cols.cap=1, fig.cap = "Experiment 1 shows decreases in algorithmic complexity (measured by the Block Decomposition Method) across transmission generations.", cache = T}
e1_chains_bdm <- all_bind_data %>%
   filter(type == "baseline", condition == "adult", trialCount > 3) %>%
  group_by(generation, seed) %>%
  summarise(empirical_stat = mean(bdm_mean))

e1_mean_bdm <- e1_chains_bdm %>%
  tidyboot_mean(empirical_stat)
  
ggplot(e1_mean_bdm, aes(x = generation, y = empirical_stat)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), data = e1_mean_bdm,
                  color = ptol_pal()(1), size = 0.3) + 
  geom_smooth(se = F, color = ptol_pal()(1), method = "lm") +
  ylab("Algorithmic complexity") +
  scale_x_continuous(limits = c(1,6), breaks=seq(1,6), name = "Generation") 
```

# Experiment 2: Replication and extension of Experiment 1

Experiment 2 replicated the task from Experiment 1 with the addition of twice as many chains and generations. The purpose of this replication was primarily to approximate the shape of the algorithmic complexity curve.

## Method
```{r n_thrown}
adult_baseline_rep <- read_csv("../../data/adult_baseline_rep.csv") %>%
  filter(generation > 0)

e2_data <- all_data %>% filter(type == "baseline_rep") %>%
  distinct(unique_id, seed, generation) %>%
  filter(generation > 0)

e2_generations <- max(e2_data$generation)
e2_seeds <- max(e2_data$seed) - 1

```
  
## Participants 

Participants in Experiment 2 were `r nrow(adult_baseline_rep)` adults recruited on Amazon Mechanical Turk. These participants were dived into `r e2_seeds %>% words` diffusion chains, each of which had `r e2_generations %>% words` generations. Each participant gave informed consent and was compensated with $0.50 for their participation in this 8-minute task.

## Design and Procedure

The task in Experiment 2 was identical to Experiment 1. Participants were told to reproduce patterns on a grid, and their responses were passed to the next subject in the transmission chain. 

Approximately `r round((nrow(adult_baseline_rep %>% filter(is.na(thrown)==F))+1) / nrow(adult_baseline_rep) * 100, 0)`% (n=`r nrow(adult_baseline_rep %>% filter(is.na(thrown)==F))+1`) of participants in Experiment 2 were excluded from analysis due to failure to meet accuracy requirements on the practice trials or failure to select the complete number of cells on one or more experimental trials. This resulted in a total of `r nrow(adult_baseline_rep %>% filter(is.na(thrown)==T))-1` participants included in the analysis.  

## Results 
```{r baseline_rep models}
linear_acc_rep <- lmer(accuracy ~ generation + trialCount + (1|sub_id) + (1|trialDisplay),
                filter(model_data, type == "baseline_rep", condition == "adult"))

exponential_e2 <- lmer(bdm_mean ~ log(generation) + (1|sub_id) + (1|trialDisplay) + trialCount,
                filter(all_bind_data, type == "baseline_rep", condition == "adult"))

exponential_e2_chunk <- lmer(chunking_mean ~ log(generation) + (1|sub_id) + (1|trialDisplay) + trialCount,
                filter(all_bind_data, type == "baseline_rep", condition == "adult"))

exponential_e2_edge <- lmer(edge_mean ~ log(generation) + (1|sub_id) + (1|trialDisplay) + trialCount,
                filter(all_bind_data, type == "baseline_rep", condition == "adult"))
```

```{r baseline_rep_parameters}
linear_acc_rep_effects <- linear_acc_rep %>%
  tidy() %>%
  filter(term == "generation") %>%
  select(term, estimate, statistic, p.value)

exponential_e2_effects <- exponential_e2 %>%
  tidy() %>%
  filter(term == "log(generation)") %>%
  select(term, estimate, statistic, p.value)

exponential_e2_chunk_effects <- exponential_e2_chunk %>%
  tidy() %>%
  filter(term == "log(generation)") %>%
  select(term, estimate, statistic, p.value)

exponential_e2_edge_effects <- exponential_e2_edge %>%
  tidy() %>%
  filter(term == "log(generation)") %>%
  select(term, estimate, statistic, p.value)

```

The results of this experiment replicated those found in Experiment 1. Reproduction accuracy increased significantly over generations, as shown by Figure \ref{fig:e2_acc_plot} ($\beta =$ `r linear_acc_rep_effects %>% pull(estimate) %>% round(3)`, $t =$ `r linear_acc_rep_effects %>% pull(statistic) %>% round(3)`, $p =$ `r linear_acc_rep_effects %>% pull(p.value) %>% printp`). 
  
Figure \ref{fig:e2_withplots} shows the results for algorithmic complexity. Algorithmic complexity appeared to follow an exponential function of the form $y = e^{-x} + b$. We therefore fit an exponential mixed-effects regression model predicting complexity from fixed effects of generation and trial number, and random intercepts for participant, and initial grid (e.g. \texttt{log(complexity) $\sim$ log(generation+1) + trial + (1|subject) + (1|initial)}). Algorithmic complexity decreased and asymptoted over generations ($\beta_{BDM} =$ `r exponential_e2_effects %>% pull(estimate) %>% round(3)`, $t =$ `r exponential_e2_effects %>% pull(statistic) %>% round(3)`, $p =$ `r exponential_e2_effects %>% pull(p.value) %>% printp`). Similar trends were also found with chunking and edge length, the alternate measures of complexity ($\beta_{chunking} =$ `r exponential_e2_chunk_effects %>% pull(estimate) %>% round(3)`, $t =$ `r exponential_e2_chunk_effects %>% pull(statistic) %>% round(3)`, $p =$ `r exponential_e2_chunk_effects %>% pull(p.value) %>% printp`; $\beta_{edge} =$ `r exponential_e2_edge_effects %>% pull(estimate) %>% round(3)`, $t =$ `r exponential_e2_edge_effects %>% pull(statistic) %>% round(3)`, $p =$ `r exponential_e2_edge_effects %>% pull(p.value) %>% printp`). As in Experiment 1, Trial Number was not a significant predictor in any model.

```{r e2_acc_plot, fig.env = "figure", fig.align='center', set.cap.width=T, fig.height = 2, fig.width = 3.4, num.cols.cap=1, fig.cap = "Experiment 2 shows increases in transmission accuracy over generations."}
acc_data <- model_data %>%
  filter(type=="baseline_rep") %>%
  filter(trialCount > 3) %>%
  group_by(generation, sub_id, type, condition) %>%
  summarise(accuracy = mean(accuracy)) %>%
  group_by(generation,type, condition) %>%
  tidyboot_mean(accuracy) 

ggplot(acc_data, aes(x = generation, y = empirical_stat, ymin = ci_lower, ymax = ci_upper)) +
  geom_pointrange(position = position_dodge(.25), color=colors[2], size =0.3)+
  geom_smooth(se = F, color = colors[2], method = "lm") +
  ylab("accuracy") +
  scale_x_continuous(breaks=seq(0,12)) +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none") 
```


```{r e2_bdm_plot, fig.env = "figure", fig.align='center', set.cap.width=T, fig.height = 2, fig.width = 3.4, num.cols.cap=1, fig.cap = "Experiments 1 and 2 show increases in accuracy over transmission generations.CHANGE POINT SIZE", cache = T, eval=T}
e2_chains_bdm <- all_bind_data %>%
   filter(type == "baseline_rep", condition == "adult", trialCount > 3) %>%
  group_by(generation, seed) %>%
  summarise(empirical_stat = mean(bdm_mean))

e2_mean_bdm <- e2_chains_bdm %>%
  tidyboot_mean(empirical_stat)
 
ggplot(e2_mean_bdm, aes(x = generation, y = empirical_stat)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), data = e2_mean_bdm,
                  color = ptol_pal()(1), size = 0.3) + 
  geom_smooth(se = F, color = colors[2], method = "lm", formula = "y~log(x)") +
  ylab("Algorithmic complexity") +
  scale_x_continuous(limits = c(1,12), breaks=seq(0,12), name = "Generation")

#+
  # theme_classic(base_size = 20) +
  # scale_y_continuous(limits=c(205,235))
```

```{r e2_withplots, fig.env = "figure", fig.align='center', set.cap.width=T, fig.height = 2.5, fig.width = 8, num.cols.cap=1, fig.cap = "Experiment 2 shows a decrease in algorithmic complexity of the grid patterns across generations. Examples of the patterns produced by participants are shown for Generation 0 (the initial, randomly-generated pattern), Generation 6, and Generation 12.", fig.show='hold', eval = F, cache = T}
img <- png::readPNG("figs/baseline_rep_comp_withplots3.png")
grid::grid.raster(img)
```

# Experiment 3: Introducing an interlocutor
  In order to add an element of feedback from a more experienced interlocutor to the iterated-learning process, we adapted the task from Experiments 1 and 2 to include a secondary, "editing" participant. This participant was analogous to a caregiver who protects their child from acquiring and perpetuating incorrect linguistic forms.
    
## Method
```{r e3_data}
adult_dyad_rep <- read_csv("../../data/dyad_rep.csv") %>%
  filter(generation > 0) %>%
  filter(seed != 3)

e3_data <- all_data %>% filter(type == "dyad_rep") %>%
  distinct(unique_id, seed, generation) %>%
  filter(generation > 0)

e3_generations <- max(e3_data$generation)
e3_seeds <- max(e3_data$seed)-2
```

## Participants

Participants in Experiment 3 were `r nrow(adult_dyad_rep)` adults recruited on Amazon Mechanical Turk. These participants were dived into `r e3_seeds %>% words` diffusion chains, each of which had `r e3_generations %>% words` generations. Each participant gave informed consent and was compensated with $0.50 for their participation.

## Design and Procedure 
  In the third, dyad experiment, a primary participant was designated to be a "learner" and completed the same task as in Experiment 1 and Experiment 2. They were told to re-produce patterns on a grid. A secondary participant -- the "fixer" -- was given an adapted task. Throughout the study, fixers were not told to re-create patterns, but to fix patterns to resemble a target grid exactly. Fixers in this experiment viewed the same target grid as learners, but instead of seeing an empty input grid, they saw a grid with 10 elements filled in – the elements that the previous learner had submitted. The participant could then edit the 10 items' positions. There was no “reset” button during this task, so data reflect participants' initial instincts. 

In Experiment 3, a generation consisted of a learner, who re-created the target grid, and a fixer, who then received the same target grid as well as the learner’s input grid to edit. The fixer’s edited pattern was used as the target grid for the subsequent generation. 

Approximately `r round((nrow(adult_dyad_rep %>% filter(is.na(thrown)==F))) / nrow(adult_dyad_rep) %>% round(1) * 100, 0)`% (n=`r nrow(adult_dyad_rep %>% filter(is.na(thrown)==F))-7` of participants in Experiment 3 were excluded from analysis due to failure to meet accuracy requirements on the practice trials or failure to select the necessary number of targets on one or more experimental trials. This resulted in a total of `r nrow(adult_dyad_rep %>% filter(is.na(thrown)==T))+7` participants included in the analysis.  

## Analysis and Results
```{r accuracy}
dyad_acc <- lmer(accuracy ~  condition + log(generation) + (1|sub_id) + (1|trialDisplay) + (1|trialCount),
                filter(model_data, type == "dyad_rep"))

fixer_acc <- lmer(accuracy ~  log(generation) + (1|sub_id) + (1|trialDisplay) + (1|trialCount),
                filter(model_data, type == "dyad_rep", condition == "adult"))

learner_acc <- lmer(accuracy ~  log(generation) + (1|sub_id) + (1|trialDisplay) + (1|trialCount),
                filter(model_data, type == "dyad_rep", condition == "child"))
```

```{r accuracy_effects}
dyad_acc_effects <- dyad_acc %>%
  tidy() %>%
  filter(term == "conditionchild") %>%
  select(term, estimate, statistic, p.value)

fixer_acc_effects <- fixer_acc %>%
  tidy() %>%
  filter(term == "log(generation)") %>%
  select(term, estimate, statistic, p.value)

learner_acc_effects <- learner_acc %>%
  tidy() %>%
  filter(term == "log(generation)") %>%
  select(term, estimate, statistic, p.value)
```

```{r complexity}
exponential_dyad_adult <- lmer(log(bdm_mean) ~ log(generation) + (1|sub_id) + (1|trialDisplay) + trialCount,
                filter(all_bind_data, type == "dyad_rep", condition == "adult"))

exponential_dyad_child <- lmer(log(bdm_mean) ~ log(generation) + (1|sub_id) + (1|trialDisplay) + trialCount + (1|seed),
                filter(all_bind_data, type == "dyad_rep", condition == "child"))

dyad_comp <- lmer(bdm_mean ~  condition + log(generation) + (1|sub_id) + (1|trialDisplay) + trialCount + (1|seed),
                filter(all_bind_data, type == "dyad_rep"))

```

```{r complexity_effects}
exponential_dyad_adult_effects <- exponential_dyad_adult %>%
  tidy() %>%
  filter(term == "log(generation)") %>%
  select(term, estimate, statistic, p.value)

exponential_dyad_child_effects <- exponential_dyad_child %>%
  tidy() %>%
  filter(term == "log(generation)") %>%
  select(term, estimate, statistic, p.value)

dyad_comp_effects_1 <- dyad_comp %>%
  tidy() %>%
  filter(term == "conditionchild") %>%
  select(term, estimate, statistic, p.value)

dyad_comp_effects_2 <- dyad_comp %>%
  tidy() %>%
  filter(term == "log(generation)") %>%
  select(term, estimate, statistic, p.value)
```

As in Experiments 1 and 2, our primary measures of analysis were accuracy and complexity. These measures were computed using the same methods as in the previous experiments. 

Fixers and learners had significantly different pattern reproduction accuracies \ref{fig:dyad_accuracy}. According to a linear mixed-effects model predicting group from generation and Trial Number and controlling for random effects of subject and initial grid. Reproduction accuracies between groups were significantly different ($\beta_{condition-child} =$ `r dyad_acc_effects %>% pull(estimate) %>% round(3)`, $t =$ `r dyad_acc_effects %>% pull(statistic) %>% round(3)`, $p =$ `r dyad_acc_effects %>% pull(p.value) %>% printp`). Neither the fixers' or learners' transmission accuracies increased significantly over generations ($\beta_{fixers} =$ `r fixer_acc_effects %>% pull(estimate) %>% round(3)`, $t =$ `r fixer_acc_effects %>% pull(statistic) %>% round(3)`, $p =$ `r fixer_acc_effects %>% pull(p.value) %>% printp`; $\beta_{learners} =$ `r learner_acc_effects %>% pull(estimate) %>% round(3)`, $t =$ `r learner_acc_effects %>% pull(statistic) %>% round(3)`, $p =$ `r learner_acc_effects %>% pull(p.value) %>% printp`). 

\ref{fig:e3_complexity_condition} shows the relationship between the complexity of fixers' and learners' patterns. In each generation, the learner decreases the complexity of the pattern, and the fixer is able to compensate for some of this loss. AS in Experiment 2, we fit an exponential model to the data. Both conditions show decreases in pattern complexity over generations ($\beta_{learners} =$ `r exponential_dyad_child_effects %>% pull(estimate) %>% round(3)`, $t =$ `r exponential_dyad_child_effects %>% pull(statistic) %>% round(3)`, $p =$ `r exponential_dyad_child_effects %>% pull(p.value) %>% printp`; $\beta_{fixers} =$ `r exponential_dyad_adult_effects %>% pull(estimate) %>% round(3)`, $t =$ `r exponential_dyad_adult_effects %>% pull(statistic) %>% round(3)`, $p =$ `r exponential_dyad_adult_effects %>% pull(p.value) %>% printp`), although the effect of generation is stronger for learners compared to fixers ($\beta_{generation} =$ `r dyad_comp_effects_2 %>% pull(estimate) %>% round(3)`, $t =$ `r dyad_comp_effects_2 %>% pull(statistic) %>% round(3)`, $p =$ `r dyad_comp_effects_2 %>% pull(p.value) %>% printp`). These results hold true for all three measures of complexity *DO ALL OF THESE STATS NEED TO BE PUT IN*.

\ref{fig:both_complexity} shows that the presence of an editor does help retain complexity in the grid patterns. The addition of a fixer into the task allowed a higher degree of complexity to be retained in the language over time ($\beta_{condition-child} =$ `r dyad_comp_effects_1 %>% pull(estimate) %>% round(3)`, $t =$ `r dyad_comp_effects_1 %>% pull(statistic) %>% round(3)`, $p =$ `r dyad_comp_effects_1 %>% pull(p.value) %>% printp`). Additionally, the patterns in the dyad condition asymptoted earlier than in the baseline condition *(Stats for this?)*. 

```{r dyad_accuracy, fig.env = "figure", fig.align='center', set.cap.width=T, fig.height = 2, fig.width = 3.4, num.cols.cap=1, fig.cap = "In Experiment 3, fixers show significantly higher reproduction accuracies than learners. Reproduction accuracies stay relatively constant, although the accuracies of the learners increase across generations.", cache = T}
acc_data <- model_data %>%
  filter(type =="dyad_rep") %>%
  mutate(type=ifelse(condition == "adult", "Fixer", "Learner"),
         type = factor(type, levels = c("Learner", "Fixer")))%>%
  filter(trialCount > 3) %>%
  group_by(generation, sub_id, type, condition) %>%
  summarise(accuracy = mean(accuracy)) %>%
  group_by(generation,type, condition) %>%
  tidyboot_mean(accuracy) 

ggplot(acc_data, aes(x = generation, y = empirical_stat, ymin = ci_lower, 
                     ymax = ci_upper, color = type, label = type)) +
  geom_pointrange(position = position_dodge(.25), size=0.3)+
  geom_smooth(se = F, aes(group=type), method = "lm", formula = "y ~ log(x)")+
  ylab("accuracy") +
  scale_x_continuous(breaks=seq(1,12)) +
  scale_color_manual(values = colors[3:4]) +
  theme(legend.position = "none") + 
  annotate("text", x = 4.75, y =.8, label = "Fixer", color = colors[4]) + 
  annotate("text", x = 4.75, y = .525, label = "Learner", color = colors[3])
```

```{r e3_complexity_condition, fig.env = "figure", fig.align='center', set.cap.width=T, fig.height = 2, fig.width = 3.4, num.cols.cap=1, fig.cap = "In Experiment 3, algorithmic complexity decreases and asymptotes for both Learners and Fixers. Learners have consistently lower complexity values compared to Fixers.", cache = T}
e3_chains_bdm <- all_bind_data %>%
  filter(type == "dyad_rep", trialCount > 3) %>%
  mutate(condition = ifelse(condition == "adult", "Fixer", "Learner"),
         condition = factor(condition, levels = c("Learner", "Fixer")))%>%
  group_by(generation, seed, condition) %>%
  summarise(empirical_stat = mean(bdm_mean))

e3_mean_bdm <- e3_chains_bdm %>%
  group_by(generation, condition) %>%
  tidyboot_mean(empirical_stat)
  
ggplot(e3_mean_bdm, aes(x = generation, y = empirical_stat, group=condition, color=condition, label=condition)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size=0.3) + 
  geom_smooth(method = "lm", formula = "y ~ log(x)", se = F) +
  ylab("Algorithmic complexity") +
  scale_color_manual(values = colors[3:4]) +
  scale_x_continuous(limits = c(1,12), breaks = 1:12, name = "Generation") +
  theme(legend.position = "none") + 
  annotate("text", x = 8, y = 227, label = "Fixer", color = colors[4]) + 
  annotate("text", x = 9, y = 215, label = "Learner", color = colors[3])
```

```{r both_complexity, fig.env = "figure", fig.align='center', set.cap.width=T, fig.height = 2.5, fig.width = 3, num.cols.cap=1, fig.cap = "The fixer's reproductions from Experiment 3 show greater levels of algorithmic complexity across generations compared to the participants' reproductions from Experiment 2.", cache = T}
e4_chains_bdm <- all_bind_data %>%
  filter((type == "dyad_rep" & condition == "adult") | type=="baseline_rep", trialCount > 3) %>%
  mutate(type = ifelse(type != "dyad_rep", "Exp 2", "Exp 3: w/Fixer"),
         type = factor(type, levels = c("Exp 2", "Exp 3: w/Fixer")))%>%
  group_by(generation, seed, type) %>%
  summarise(empirical_stat = mean(bdm_mean))

e4_mean_bdm <- e4_chains_bdm %>%
  group_by(generation, type) %>%
  tidyboot_mean(empirical_stat)

ggplot(e4_mean_bdm, aes(x = generation, y = empirical_stat, group=type, color=type, label=type)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size=0.3) + 
  geom_smooth(method = "lm", formula = "y ~ log(x)", se = F) +
  ylab("Algorithmic complexity") +
  scale_x_continuous(limits = c(1,12), name = "Generation", breaks = 1:12) +
  theme_classic(base_size = 10) +
  scale_color_manual(values = c(colors[2], colors[4])) +
#  geom_dl(method = list(dl.trans( x=x+0.2, y=y-0.2), "last.points", cex = 0.65)) + 
  theme(legend.position = "none") + 
  annotate("text", x = 7.5, y = 212, label = "Exp2", color = colors[2]) + 
  annotate("text", x = 9, y = 220, label = "Exp3: w/Fixer", color = colors[4])
```

# General Discussion

Despite the use of a non-linguistic task in Experiments 1-3, we were able to measure change in a culturally-transmitted, learned symbol system. In Experiments 1 and 2, language simplified rapidly and dramatically, reflecting the strong pressure towards simplification in language learning. These findings replicated those of @kempe-2015: when transmitting an artificial language of grid patterns, complexity in the language was lost.

However, the results of Experiment 3 show that this loss is not cultural regression, as complexity can be reintroduced in the language by way of a secondary participant. When the iterated-learning process begins to resemble the true process of language-learning, where children speak with and are subject to correction by those more competent in the language, a lesser amount of complexity was lost during transmission. Additionally, this stable level of complexity was much higher, and was reached earlier in the transmission chain with the help of a fixing participant. This stability in complexity did not mean that the language stopped changing, but that the descriptiveness and transmissibility pressures were in balance. Fixers in Experiment 3 represented caregivers -- they were more accurate at reproducing the language, and could therefore be seen as more fluent speakers, just as adults are of their native languages. The learners, on the other hand, had a more difficult task, which greater strained their working memories, similar to the strain on a child language learner who is inundated with new words each day. The fixer's corrected language was passed to the next learner in the chain, representing a child who, after many years of being corrected by their own parent, becomes a parent, and, in turn, passes their optimal language to the next generation. Due to the higher accuracy by fixers, and therefore greater knowledge of the language, the fixers were able to compensate for some (not all) of the learners' losses in complexity. 

When a caregiver or teacher prevents their child from growing up to believe that "baba" is the word for both "bottle" and "sheep", they are not only helping their individual child become a competent speaker of the language, but they are also reintroducing complexity, thus helping the language system as a whole from simplifying to disuse. Data collection is ongoing with children ages 6-8 at a local science museum in both the Experiment 1 and Experiment 3 tasks, in order to investigate whether the pressures of similarity and complexity affect children similarly to how they affect adults in early language-learning conditions.

We do not learn language as passive listeners, who absorb a proportion of the linguistic input they hear. Therefore, we cannot measure language learning only through measuring input, nor through measuring only linguistic output. Languages are both learned and changed through conversations to evolve to the needs of the language's users. Therefore, we must study language learning in process, to see how it adapts and evolves with communicative interactions.

# References 
```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}

\noindent
