---
title: "iterated_learning"
author: "Maddie Meyers, Dan Yurovsky"
date: "7/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(tidyverse)
library(png)
library(grid)
library(xtable)
library(feather)
library(irr)
library(tidyboot)
library(directlabels)
library(lme4)
library(broom)
library(acss)
library(devtools)
library(reshape2)

theme_set(theme_classic(base_size = 10))
```

## Setup

Loading functions -- OLD 
```{r load csv}
data2 <- read_csv("../data/anonymized_data.csv")
kidData<-read_csv("iteratedstudyresults.csv")
practice_data <- matrix(sample(0:1, 64, replace=TRUE), nrow=8, ncol=8)

#filters out people who didn't complete 10 trials
data <- data2 %>%
#data<-kidData %>%
 arrange(sub_id, trialDisplay) %>%
  group_by(sub_id) %>%
  mutate(n = n()) %>%
  filter(n >= 12 & condition != "test" & sub_id != 0) %>%
 # filter(condition == "pilotkid" & sub_id != "Xx" & sub_id != "sdgd" & sub_id != 1) %>%
  select(-n) %>%
  ungroup() %>%
  filter(trialCount < 14)
```
format data -- OLD
```{r}
spread_data <- data %>%
  gather(row, value, -sub_id, -age, -condition, -generation, -date, -time, -trialDisplay, -trialCount, -comments)%>%
  arrange(sub_id, trialDisplay) %>%
  separate(row, c("type","row", "col")) %>%
  unite(ty_col, type, col) %>%
  spread(ty_col, value) %>%
  filter(is.na(row)==F)
```
--Format data OLD
```{r formats data}
calculate_data <- data %>%
  gather(row, value,-sub_id:-trialDisplay)%>%
  arrange(sub_id, trialDisplay) %>%
  separate(row, c("type","row", "col")) %>%
  spread(type,value) %>%
  mutate(input = as.numeric(input), target = as.numeric(target),
         row = as.numeric(row), column = as.numeric(col)) %>%
  mutate(accuracy = input == target,
         sub_id = as.character(sub_id)) 
```


## Read in Data from Google Sheet (Pilot)
```{r read in data from google sheet}
data_sheet <- gs_ls() %>%
  filter(sheet_title == "Kid Generations") %>%
  pull(sheet_key) %>%
  gs_key() %>%
  gs_read(ws = "Sheet1") %>%
  filter(seed == 1 & condition == "adult_baseline_pilot") #filter to just this pilot seed data 
```

## Read in Adult Baseline Data (saved as .csv taken from Google Sheet, includes only full chains)
```{r read in data}
adult_baseline <- read_csv("../data/adult_baseline.csv") %>%
  select(-sum_timeUsed)

```


## Format Data for Display & Grid Analysis - New
```{r}
tmp_data <- adult_baseline %>% #puts each trial and either target or display in a separate row
  select(-available_onload, -available_accepted, -sub_age) %>%
  gather(display, array, -unique_id, -parent_id, -child_id, -sub_id, -generation, -seed, -condition, -date, -time, -trial1Count, -time1Used, -trial1Display, -trial2Count, -time2Used, -trial2Display, -trial4Count, -trial4Display, -time4Used, -trial5Count, -trial5Display, -time5Used, -trial6Count, -trial6Display, -time6Used, -trial7Count, -trial7Display, -time7Used, -trial8Count, -trial8Display, -time8Used, -trial9Count, -trial9Display, -time9Used) %>%
  arrange(sub_id) %>%
  unique() %>%
  separate(display, c("type", "trialCountArray"), -6) %>%
  separate(trialCountArray, c("trialCount", "arrayCount"), 1) %>%
  select(-arrayCount, -trial1Count, -trial2Count, -trial4Count, -trial5Count, -trial6Count, -trial7Count, -trial8Count, -trial9Count) %>%
  gather(trialDisplay, display, -unique_id, -parent_id, -child_id, -sub_id, -generation, -seed, -condition, -date, -time, -time1Used, -time2Used, -time4Used, -time5Used, -time6Used, -time7Used,  -time8Used,-time9Used, -type, -trialCount, -array) %>%
  separate(trialDisplay, c("type2", "tmp"), -7) %>%
  select(-tmp) %>%
  separate(type2, c("tmp", "trialCount2"), -1) %>%
  select(-tmp) %>%
  filter(trialCount2 == trialCount) %>%
  select(-trialCount2, trialDisplay = display) %>%
  gather(trialTime, timeUsed, -unique_id, -parent_id, -child_id, -sub_id, -generation, -seed, -condition, -date, -time, -type, -trialCount, -trialDisplay, -array) %>%
  separate(trialTime, c("tmp", "trialCount3"), -5) %>%
  separate(trialCount3, c("trialCount3", "tmp2"), 1) %>%
  select(-tmp, -tmp2) %>%
  filter(trialCount == trialCount3) %>%
  select(unique_id, parent_id, child_id, sub_id, generation, seed, condition, date, time, trialCount, trialDisplay, timeUsed, type, array) %>%
  spread(type, array) %>%
  separate(data, c("input_0_0", "input_0_1", "input_0_2", "input_0_3", "input_0_4", "input_0_5", "input_0_6", "input_0_7", "input_1_0", "input_1_1", "input_1_2", "input_1_3", "input_1_4", "input_1_5", "input_1_6", "input_1_7", "input_2_0", "input_2_1", "input_2_2", "input_2_3", "input_2_4", "input_2_5", "input_2_6", "input_2_7", "input_3_0", "input_3_1", "input_3_2", "input_3_3", "input_3_4", "input_3_5", "input_3_6", "input_3_7", "input_4_0", "input_4_1", "input_4_2", "input_4_3", "input_4_4", "input_4_5", "input_4_6", "input_4_7", "input_5_0", "input_5_1", "input_5_2", "input_5_3", "input_5_4", "input_5_5", "input_5_6", "input_5_7", "input_6_0", "input_6_1", "input_6_2", "input_6_3", "input_6_4", "input_6_5", "input_6_6", "input_6_7", "input_7_0", "input_7_1", "input_7_2", "input_7_3", "input_7_4", "input_7_5", "input_7_6", "input_7_7"), sep = " ") %>%
    separate(target, c("target_0_0", "target_0_1", "target_0_2", "target_0_3", "target_0_4", "target_0_5", "target_0_6", "target_0_7", "target_1_0", "target_1_1", "target_1_2", "target_1_3", "target_1_4", "target_1_5", "target_1_6", "target_1_7", "target_2_0", "target_2_1", "target_2_2", "target_2_3", "target_2_4", "target_2_5", "target_2_6", "target_2_7", "target_3_0", "target_3_1", "target_3_2", "target_3_3", "target_3_4", "target_3_5", "target_3_6", "target_3_7", "target_4_0", "target_4_1", "target_4_2", "target_4_3", "target_4_4", "target_4_5", "target_4_6", "target_4_7", "target_5_0", "target_5_1", "target_5_2", "target_5_3", "target_5_4", "target_5_5", "target_5_6", "target_5_7", "target_6_0", "target_6_1", "target_6_2", "target_6_3", "target_6_4", "target_6_5", "target_6_6", "target_6_7", "target_7_0", "target_7_1", "target_7_2", "target_7_3", "target_7_4", "target_7_5", "target_7_6", "target_7_7"), sep = " ") 

calculate_data <-tmp_data %>%
    gather(row, value,-unique_id:-timeUsed)%>%
  arrange(sub_id, trialDisplay) %>%
  separate(row, c("type","row", "col")) %>%
  spread(type,value) %>%
  mutate(input = as.numeric(input), target = as.numeric(target),
         row = as.numeric(row), column = as.numeric(col)) %>%
  mutate(accuracy = input == target,
         sub_id = as.character(sub_id)) %>%
  arrange(seed, generation) 


spread_data <- tmp_data %>%
  gather(row, value, -unique_id, -parent_id, -child_id, -sub_id, -condition, -generation, -seed, -date, -time, -trialDisplay, -trialCount, -timeUsed)%>%
  arrange(sub_id, trialDisplay) %>%
  separate(row, c("type","row", "col")) %>%
  unite(ty_col, type, col) %>%
  spread(ty_col, value) %>%
  filter(is.na(row)==F)


tmp <- tmp_data %>%
  #select(-(unique_id:time)) %>%
#  select(-timeUsed, -trialCount) %>%
  select(-trialCount) %>%
  unique() %>%
  ungroup() %>%
  arrange(trialDisplay, generation)
```

## Descriptive
Displays the actual grids that people made 
```{r plot_grids}
pdf("trial_data_adults_s22.pdf", width = 10, height = 10)
calculate_data %>%
  bind_rows(select(calculate_data, generation, trialDisplay, row, col, input)) %>%
  mutate(input = factor(input), generation = factor(generation, levels = unique(.$generation))) %>%
  mutate(row = 7 - row) %>%
  ggplot(aes(x = col, y = row, fill = input)) +
  facet_grid(trialDisplay ~ generation) +
  geom_tile(color = "black") +
  scale_fill_manual(values = c("0" = "white", "1" = "black"), guide = F) 
dev.off()
```

## Analysis
Percent accuracies calculated by %/10 targets placed correctly 
```{r accuracy}
trial_data <- calculate_data %>%
  filter(generation != 0) %>%
  filter(trialDisplay > 0) %>%
 # filter(sub_id == 5 | sub_id == 2) %>%
  group_by(trialCount, sub_id) %>%
  summarise(accuracy = mean(accuracy)) %>%
  tidyboot_mean(accuracy) 

ggplot(trial_data, aes(x = trialCount, y = empirical_stat, 
                       ymin = ci_lower, ymax = ci_upper)) + 
  geom_pointrange() + 
  geom_smooth()
```

Clustering: # of identifiable touching "parts"(excluding diagonals). This function was taken from Gauvrit et al 2017. 
```{r}

```

Density: measured as edge length. Taken from Gauvrit et al 2017
```{r}

```

Want a function that can summarize over every set of 8 rows 
```{r}
bdm_function = function(m){
  x = rep("x", nrow(m)/8)
  k=1
  q=1
  for(i in 1:(nrow(m)/8)){
    df = m[q:(q+7), 5:12]
    data.matrix(df)
    x[k] = bdm(df)
    k = k +1
    q=q+8
  }
  return(x) 
}
```

```{r}
nPart_function = function(m){
  x = rep("x", nrow(m)/8)
  k=1
  q=1
  for(i in 1:(nrow(m)/8)){
    df = m[q:(q+7), 5:12]
    data.matrix(df)
    x[k] = nPart(df)
    k = k +1
    q=q+8
  }
  return(x) 
}
```

```{r}
edge_function = function(m){
  x = rep("x", nrow(m)/8)
  k=1
  q=1
  for(i in 1:(nrow(m)/8)){
    df = m[q:(q+7), 5:12]
    data.matrix(df)
    x[k] = edge(df)
    k = k +1
    q=q+8
  }
  return(x) 
}
```

Algorithmic Complexity: Block Decomposition Method [do you need to install the function every time?]
```{r}
bdm_data <- spread_data %>%
  filter(trialDisplay != 0, is.na(sub_id)==FALSE) %>%
  select(sub_id, generation, trialDisplay, row, input_0:input_7) %>%
  mutate(input_7 = as.numeric(input_7),
         input_6 = as.numeric(input_6),
         input_5 = as.numeric(input_5),
         input_4 = as.numeric(input_4),
         input_3 = as.numeric(input_3),
         input_2 = as.numeric(input_2),
         input_1 = as.numeric(input_1),
         input_0 = as.numeric(input_0)) 

target_data <- spread_data %>%
  filter(trialDisplay != 0 & trialDisplay != 0.5 & generation == 0)  %>%
  select(sub_id, generation, trialDisplay, row, input_0:input_7) %>%
  mutate(sub_id = 0) %>%
  mutate(target_0 = as.numeric(input_7),
         target_1 = as.numeric(input_6),
         target_2 = as.numeric(input_5),
         target_3 = as.numeric(input_4),
         target_4 = as.numeric(input_3),
         target_5 = as.numeric(input_2),
         target_6 = as.numeric(input_1),
         target_7 = as.numeric(input_0)) %>%
  select(-(input_0:input_7)) %>%
  arrange(trialDisplay,row) %>%
  unique()
 
target_store <- data.frame(bdm = bdm_function(target_data),
                           chunking = nPart_function(target_data),
                           edge = edge_function(target_data)) 
bdm_store <- data.frame(bdm = bdm_function(bdm_data),
                        chunking = nPart_function(bdm_data),
                        edge = edge_function(bdm_data))

bind_targets <- target_data %>%
  mutate(generation = 0) %>%
  group_by(sub_id, trialDisplay, generation) %>%
  summarise(.) %>%
  bind_cols(target_store, .)

bind_data <- bdm_data %>%
  group_by(sub_id, trialDisplay, generation) %>%
  summarise(.) %>%
  bind_cols(bdm_store, .) %>%
  bind_rows(. , bind_targets) %>%
  mutate(bdm = as.numeric(bdm),
         chunking = as.numeric(chunking),
         edge = as.numeric(edge)) %>%
  group_by(sub_id, trialDisplay, generation)%>%
  summarise(bdm_mean = mean(bdm),
            chunking_mean = mean(chunking),
            edge_mean = mean(edge)) %>%
  group_by(trialDisplay, generation) %>%
  #group_by(generation) %>%
  #tidyboot_mean(bdm_mean) 
  #tidyboot_mean(chunking_mean)
  tidyboot_mean(edge_mean)

```

```{r display complexity values}
ggplot(bind_data, aes(x = trialDisplay, y = empirical_stat, 
                       ymin = ci_lower, ymax = ci_upper)) + 
  geom_pointrange() + facet_wrap(~generation) + geom_smooth()


ggplot(bind_data, aes(x=generation, y=bdm_mean)) + geom_point()
```

```{r}
target_store <- data.frame(b = bdm_function(target_data)) 
bdm_store <- data.frame(bdm = bdm_function(bdm_data))

bind_targets <- target_data %>%
  mutate(generation = 0) %>%
  group_by(sub_id, trialDisplay, generation) %>%
  summarise(.) %>%
  bind_cols(target_store, .)

bind_data <- bdm_data %>%
  group_by(sub_id, trialDisplay, generation) %>%
  summarise(.) %>%
  bind_cols(bdm_store, .) %>%
  bind_rows(. , bind_targets) %>%
  mutate(bdm = as.numeric(bdm)) %>%
  group_by(sub_id, trialDisplay, generation)%>%
  summarise(bdm_mean = mean(bdm)) %>%
  group_by(trialDisplay, generation) %>%
  #group_by(generation) %>%
  tidyboot_mean(bdm_mean) 

```

