---
title: "iterated_learning"
author: "Maddie Meyers, Dan Yurovsky"
date: "7/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(tidyverse)
library(png)
library(grid)
library(xtable)
library(feather)
library(irr)
library(tidyboot)
library(directlabels)
library(lme4)
library(broom)
library(acss)
library(devtools)

theme_set(theme_classic(base_size = 10))
```

## Setup

```{r load csv}
data2 <- read_csv("../data/anonymized_data.csv")
kidData<-read_csv("iteratedstudyresults.csv")
practice_data <- matrix(sample(0:1, 64, replace=TRUE), nrow=8, ncol=8)
practice_data_2<-rbind(practice_data, matrix(sample(0:1,100, replace=TRUE), nrow=10, ncol=10))

#filters out people who didn't complete 10 trials
data <- data2 %>%
#data<-kidData %>%
 arrange(sub_id, trialDisplay) %>%
  group_by(sub_id) %>%
  mutate(n = n()) %>%
  filter(n >= 12 & condition != "test" & sub_id != 0) %>%
 # filter(condition == "pilotkid" & sub_id != "Xx" & sub_id != "sdgd" & sub_id != 1) %>%
  select(-n) %>%
  ungroup() %>%
  filter(trialCount < 14)
```

```{r formats data}
calculate_data <- data %>%
  gather(row, value,-sub_id:-trialDisplay)%>%
  arrange(sub_id, trialDisplay) %>%
  separate(row, c("type","row", "col")) %>%
  spread(type,value) %>%
  mutate(input = as.numeric(input), target = as.numeric(target),
         row = as.numeric(row), column = as.numeric(col)) %>%
  mutate(accuracy = input == target,
         sub_id = as.character(sub_id)) 
```
## Descriptive
Displays the actual grids that people made 
```{r plot_grids}
pdf("trial_data_adults.pdf", width = 10, height = 10)
calculate_data %>%
  distinct(trialDisplay, row, col, target) %>%
  mutate(sub_id = "target") %>%
  rename(input = target) %>%
  bind_rows(select(calculate_data, sub_id, trialDisplay, row, col, input)) %>%
  mutate(input = factor(input), sub_id = factor(sub_id, levels = unique(.$sub_id))) %>%
  mutate(row = 7 - row) %>%
  ggplot(aes(x = col, y = row, fill = input)) +
  facet_grid(trialDisplay ~ sub_id) +
  geom_tile(color = "black") +
  scale_fill_manual(values = c("0" = "white", "1" = "black"), guide = F)
dev.off()
```

## Analysis
Percent accuracies calculated by %/10 targets placed correctly 
```{r accuracy}
trial_data <- calculate_data %>%
  filter(target == 1) %>%
  filter(trialDisplay > 0) %>%
 # filter(sub_id == 5 | sub_id == 2) %>%
  group_by(trialCount, sub_id) %>%
  summarise(accuracy = mean(accuracy)) %>%
  tidyboot_mean(accuracy) 

ggplot(trial_data, aes(x = trialCount, y = empirical_stat, 
                       ymin = ci_lower, ymax = ci_upper)) + 
  geom_pointrange() + 
  geom_smooth()
```

Clustering: # of identifiable touching "parts"(excluding diagonals). This function was taken from Gauvrit et al 2017. 
```{r}

```

Density: measured as edge length. Taken from Gauvrit et al 2017
```{r}

```

Algorithmic Complexity: Block Decomposition Method [do you need to install the function every time?]
```{r}
one_grid <- data %>%
  filter(sub_id == 0.0666252233225888, trialCount == 4) %>%
  select(input_0_0:input_7_7)

#make a loop that looks at each 10 rows in data frame and computes the complexity bdm of each one and then spits it into data frame 
bdm(practice_data) #this does work with a random 10x10 matrix; does not work with other sized matrices 



```

